%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 

\documentclass[]{deedy-resume-openfont}

    \usepackage{fontawesome}
    \begin{document}
    
    
    
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     TITLE NAME
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    
    \namesection{}{Hitesh Roy}{ \faLink \space \href{https://hiteshroy.me/}{hiteshroy.me} \space
    \faEnvelopeO \space \href{mailto:hiteshproy@gmail.com}{hiteshproy@gmail.com} \space \faMobilePhone \space (+91) 9890272898 \space \faGithub \space \href{https://github.com/hiteshpr}{hiteshpr} \space \faLinkedin \space \href{https://www.linkedin.com/in/hiteshpr}{hiteshpr}
    }
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     COLUMN ONE
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \begin{minipage}[t]{0.32\textwidth} 
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Skills}
    \subsection{Programming Languages}
    
    JavaScript \textbullet{}   PHP \textbullet{} HTML \textbullet{} CSS \\
    C++ \textbullet{} C \textbullet{} Python \textbullet{} SQL
    \sectionsep
    
    \subsection{Frameworks \& Databases}
    Angular JS/2/6 \space \textbullet{}ExpressJS \textbullet{} CakePHP 3 \newline \textbullet{} Laravel \textbullet{} JQuery \textbullet{} Bootstrap \textbullet{} Django \newline \textbullet{} MySQL \textbullet{} MongoDB \textbullet{} Redis 
    \sectionsep
    
    \subsection{Tools}
    Git \textbullet{} Svn \textbullet{} Mantis Bug Tracking \\ \textbullet{} Postman  \textbullet{} Chrome Dev Tools \textbullet{} Jira \newline \textbullet{} Aasana \textbullet{} Slack \textbullet{} Gitter
    \sectionsep
    
    \subsection{Platforms}
    Ubuntu 14.04/16.04 \textbullet{} Windows 8.1/10 \newline \textbullet{} Arduino \textbullet{} RaspberryPI 3
    
    \sectionsep
    
    \subsection{IDE}
    Sublime Text \textbullet{} Visual Studio Code \newline \textbullet{} Notepad++ \textbullet{} Code-blocks  
    
    \sectionsep
    
    \section{Projects / Open-Source Contribution}
    
    \runsubsection{KWOC 2017}
    \descript{| \href{http://kwoc.kossiitkgp.in/} {IIT Kharagpur}}
    \textbullet\ Amongst the top contributors in the competition.\\
    \textbullet\ Successfully added PWA and carousel in systemJS  structure.\\
    \textbullet\ Integrated last-fm, Google and facebook login REST APIs.
    \sectionsep
    
    \runsubsection{Loyalty App}
    \descript{| \href{https://techchallenge.in.capgemini.com/techchallenge}{Capgemini}}
    \textbullet\ Qualified 1st round of tech challenge'18 with score of 76/100.\\
    \textbullet\ Made Subscription based e-commerce app model in ionic with nodeJS back-end for round 2. 
    \sectionsep
    
    \runsubsection{Weather App}
    \descript{| \href{ https://github.com/hiteshpr/WeatherApp}{link}}
    \textbullet\  Web App to display current weather condition and weather forecast of the place entered.\\
    \textbullet\ Used OpenWeather Map REST APIs for getting the data.\\
    \sectionsep
    
    \runsubsection{Object detection}
    \descript{| Link}
    \textbullet\  Taking webcam feed in Angular App and doing object detection using tensorflow.js. Got 80\% accuracy.\\
    \sectionsep
    
    
    
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     COLUMN TWO
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \end{minipage} 
    \hfill
    \begin{minipage}[t]{0.66\textwidth} 
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Education}
    
    \runsubsection{Government College of Engineering, Amravati (GCOEA), Maharashtra } \newline
    \descript{B.Tech in Electronics and Telecommunication Engineering}
    \location{Expected May 2019 |  CGPA- 7.30/10 (till $6^{th}$ semester)}
    \vspace{\topsep}
    \sectionsep
    
    \runsubsection{Hislop Junior College, Nagpur}
    \descript{| Maharashtra State Board }
    \location{2014 | Percentage - 83\%}
    
    \sectionsep
    
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     Internship Experience
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Experiences}
    \runsubsection{ \href{https://flytbase.com/}{FlytBase, Pune} }
    \descript{| Full Stack Development Intern }
    \location{May 2018 - Present}
    \vspace{3mm}
    \begin{tightemize}
    \item Implementing engineering major project titled 'Security and Surveillance using Drones' using MEAN stack, redis, roslib. Link - \href{https://flytsecurity.ai/}{FlytSecurity} 
     \item Worked on consumer projects FlytCloud, FlytLive and FlytOS which are used for deploying and managing drone fleet remotely. 
     \item Worked extensively with Google Maps and Airmap. Worked on streaming live drone feed using WebRTC and Twilio. Integrated Stripe payment gateway. \end{tightemize}
    
    
    \sectionsep
    
    \runsubsection{\href{https://www.healthcoco.com/}{Healthcoco, Nagpur}}
    \descript{| Frontend Intern (Part-time) }
    \location{Jan 2018 - March 2018}
    \begin{tightemize}
     \item Worked on integrating REST APIs and UI/UX development of Admin App used for managing doctors, labs and clinics in AngualrJS. \item Worked on integrating material design, session management, filters, PWA in Patient App in Angular 4. \end{tightemize}
    
    
    \sectionsep
    
    \runsubsection{\href{https://www.healthcoco.com/}{Healthcoco, Nagpur}}
    \descript{| Web Development Intern }
    \location{Nov 2017 - Dec 2017}
    
    \begin{tightemize}
     \item Integrated key modules like Patient Registration, Profile, Search doctors in the Patient Web App in Angular 2. Migrated the project to Angular 4. \item Designed, developed and deployed website for a dental clinic using PHP, MySQL, cPanel. Visit - \href{http://www.kharedentalclinic.com}{Khare Dental}  \end{tightemize}
     
    \sectionsep
    
    \runsubsection{\href{http://www.vyako.com/}{Vyako, Nagpur}}
    \descript{| Summer Intern }
    \location{January 2017 - June 2017}
    \vspace{1mm}
    \begin{tightemize}
     \item Worked on two projects in development stage - Human Resource Management System (HRMS) and Project Management. \item Responsible for development and integration of many important features in HRMS projects such as Employee Management, Leave and Attendance Management in CakePHP 3 and Laravel.  
    \end{tightemize}
    
    \sectionsep
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SOCIETIES
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{SOCIETIES \& Extra-curricular Activities} 
    \vspace{3mm}
    \begin{tightemize}
        \item Member of ACM India Nagpur chapter, google developers group Pune, PyData Pune. Founding member of GCOEA Developers club.
        \item Selected as GitHub Campus Expert, Recipient of Udacity Web Nanodegree scholarship. Undergoing 'Machine Learning using PyTorch' Nanodegree.
        \item Delivered various talks in college on technical topics and internship experience.
        \item Organized Android and Robotics related competitions in college annual technical fest.
        \item Hobbies: Learning new things in tech, Watching movies,TV series and tech shows, Playing cricket and badminton, blogging on Quora, Medium
    \end{tightemize}
    
    \sectionsep
    
    \end{minipage} 
    \end{document}