%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 

\documentclass[]{deedy-resume-openfont}

\usepackage{fontawesome}
\begin{document}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Hitesh Roy}{ \faLink \space \href{https://hiteshroy.me/}{hiteshroy.me} 
\faEnvelopeO \space \href{mailto:hiteshproy@gmail.com}{hiteshproy@gmail.com} \space \faMobilePhone \space (+91) 9890272898 \space \faGithub \space \href{https://github.com/hiteshpr}{hiteshpr} \space \faLinkedin \space \href{https://www.linkedin.com/in/hiteshpr}{hiteshpr} 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}

JavaScript \textbullet{}   PHP \textbullet{} HTML \textbullet{} CSS \\
C++ \textbullet{} C \textbullet{} Python \textbullet{} SQL \textbullet{} LATEX 
\sectionsep

\subsection{Frameworks}
Angular 2,4  \textbullet{}AngularJS \textbullet{} CakePHP 3 \newline \textbullet{} Laravel \textbullet{} Jquery \textbullet{} Bootstrap 
\sectionsep

\subsection{Tools}
Git \textbullet{} Svn \textbullet{} Mantis Bug Tracking \\ \textbullet{} Postman  \textbullet{} Chrome Dev Tools \textbullet{} Jira 
\sectionsep

\subsection{Platforms}
Ubuntu 14.04 \textbullet{} Windows 8.1 \newline \textbullet{} Windows 10 \textbullet{} Arduino IDE

\sectionsep

\subsection{IDE}
Sublime Text \textbullet{} Visual Studio Code \newline \textbullet{} Notepad++ \textbullet{} Code-blocks 

\sectionsep

\section{Projects, Open-Source Contribution}

\subsection{KWOC 2017}
\location{\href{http://kwoc.kossiitkgp.in/} {IIT Kharagpur}}
\textbullet\  Amongst the top contributors in the Open-source competition.\\
\textbullet\ Successfully added Progressive Web App (PWA) functionality.\\
\textbullet\ Integrated popular REST APIs like last-fm, Google and facebook login.
\sectionsep

\subsection{Opencode 2018}
\location{\href{https://opencode18.github.io/} {IIIT Allahabad}}
\textbullet\  Currently contributing in two projects based on NodeJs and Angular.\\
\sectionsep

\subsection{Weather App}
\location{\href{ https://github.com/hiteshpr/WeatherApp } {Personal Project}}
\textbullet\  Web App to display current weather condition and weather forecast of the place entered.\\
\textbullet\ Used OpenWeather Map REST APIs \\for getting the needed data.\\
\textbullet\ Currently working on adding Material Design and PWA functionality.
\sectionsep

\subsection{Contacts App }
\location{\href{https://github.com/hiteshpr/AngularLaravelApp} {Personal Project}}
\textbullet\  Simple Web App to Add, Update, Delete and View contact names and their Details. Backend developed
in Laravel using MySQL database.\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\runsubsection{Government College of Engineering, Amravati (GCOEA), Maharashtra } \newline
\descript{B.Tech in Electronics and Telecommunication Engineering  }
\location{2014-2019  CGPA- 7.20/10 (till $5^{th}$ semester)}
\vspace{\topsep}
\sectionsep

\runsubsection{Hislop College, Nagpur}
\descript{ Maharashtra State Board,\\ Higher Secondary Examination, }
\location{2014 Percentage - 83\%}

\sectionsep

\runsubsection{Kendriya Vidyalaya(CBSE)}
\descript{Secondary Examination,}
\location{2012 GPA - 9.8/10, Percentage - 90\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Internship Experiences}
\runsubsection{Web Development Intern (Part-time)}
\descript{\newline \href{https://www.healthcoco.com/}{Healthcoco Technologies Pvt. Ltd, Nagpur}}
\location{Jan 2018 - Present}
\vspace{3mm}
\begin{tightemize}
 \item Working on integrating REST APIs and UI development of Admin App used for managing doctors, labs and clinics in AngualrJS. \item Working on integrating material design and session management in Patient App in Angular 4. \end{tightemize}


\sectionsep

\runsubsection{Web Development Intern}
\descript{\newline \href{https://www.healthcoco.com/}{Healthcoco Technologies Pvt. Ltd, Nagpur}}
\location{Nov 2017 - Dec 2017}

\begin{tightemize}
 \item Integrated some key modules like Patient Registration, Profile, Search doctors in the Patient App in Angular 2. \item Designed, developed and deployed website for a dental clinic in core PHP.\newline Visit - \href{http://www.kharedentalclinic.com}{Khare Dental}  \end{tightemize}
 
\sectionsep

\runsubsection{Web Development Intern}
\descript{\newline \href{http://www.vyako.com/}{Vyako Technologies Pvt. Ltd, Nagpur,}}
\location{January 2017 - June 2017}

\begin{tightemize}
 \item Worked on two projects in development stage - Human Resource Management System (HRMS) and Project Management. \item Responsible for development and integration of many important features in HRMS projects such as
Employee Management, Leave Management, Attendance Management
\item Created the login and sign-up flow for Project Management. Created the home page UI and database
schema.
\end{tightemize}

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards} 
%\begin{tabular}{rll}
%2014	     & top 52/2500  & KPCB Engineering Fellow\\
%2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
%2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%2013	     & National  & Jump Trading Challenge Finalist\\
%2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%2010     & National & Comp. Soc. of India's National Programming Contest\\
%\end{tabular}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extra-curricular Activities} 
\vspace{3mm}
\begin{tightemize}
 \item Member of Andromaster organising committee in Prajwalan (annual technical festival of college).
 \item Member of Alumni website committee.
 \item Member of core committee - GCOEA Developers club, member of ACM India nagpur chapter, Google developers group Pune.
 \item Hobbies: Programming, Watching movies,TV series and tech shows, Playing cricket and badminton,
Learning new things.
\end{tightemize}

\sectionsep

\end{minipage} 
\end{document}