%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 

\documentclass[]{deedy-resume-openfont}

\usepackage{fontawesome}
\begin{document}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Hitesh Roy}{ \faLink \space \href{https://hiteshroy.me/}{hiteshroy.me} 
\faEnvelopeO \space \href{mailto:hiteshproy@gmail.com}{hiteshproy@gmail.com} \space \faMobilePhone \space (+91) 9890272898 \space \faGithub \space \href{https://github.com/hiteshpr}{hiteshpr} \space \faLinkedin \space \href{https://www.linkedin.com/in/hiteshpr}{hiteshpr} 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}

JavaScript \textbullet{}   PHP \textbullet{} HTML \textbullet{} CSS \\
C++ \textbullet{} C \textbullet{} Python \textbullet{} SQL \textbullet{} LATEX 
\sectionsep

\subsection{Frameworks}
Angular 2,4,6  \textbullet{}AngularJS \textbullet{} CakePHP 3 \newline \textbullet{} Laravel \textbullet{} Jquery \textbullet{} Bootstrap \textbullet{} Django 
\sectionsep

\subsection{Tools}
Git \textbullet{} Svn \textbullet{} Mantis Bug Tracking \\ \textbullet{} Postman  \textbullet{} Chrome Dev Tools \textbullet{} Jira \newline \textbullet{} Aasana \textbullet{} Slack \textbullet{} Gitter
\sectionsep

\subsection{Platforms}
Ubuntu 14.04, 16.04 \textbullet{} Windows 8.1, 10 \newline \textbullet{} Arduino IDE

\sectionsep

\subsection{IDE}
Sublime Text \textbullet{} Visual Studio Code \newline \textbullet{} Notepad++ \textbullet{} Code-blocks  

\sectionsep

\section{Projects/Open-Source Contribution}

\subsection{KWOC 2017}
\location{\href{http://kwoc.kossiitkgp.in/} {IIT Kharagpur}}
\textbullet\  Amongst the top contributors in the Open-source competition.\\
\textbullet\ Successfully added Progressive Web App (PWA) functionality.\\
\textbullet\ Integrated popular REST APIs like last-fm, Google and facebook login.
\sectionsep

\subsection{Opencode 2018}
\location{\href{https://opencode18.github.io/} {IIIT Allahabad}}
\textbullet\ Contributing in two projects based on NodeJs and Angular.\\
\sectionsep

\subsection{Weather App}
\location{\href{ https://github.com/hiteshpr/WeatherApp } {Personal Project}}
\textbullet\  Web App to display current weather condition and weather forecast of the place entered.\\
\textbullet\ Used OpenWeather Map REST APIs \\for getting the needed data.\\
\textbullet\ Working on adding Material Design and PWA functionality.
\sectionsep

\subsection{Contacts App }
\textbullet\  Web App to Add, Update, Delete and View contact names and their Details. Backend developed in Laravel using MySQL database.\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\runsubsection{Government College of Engineering, Amravati (GCOEA), Maharashtra } \newline
\descript{B.Tech in Electronics and Telecommunication Engineering  }
\location{2014-2019  CGPA- 7.30/10 (till $6^{th}$ semester)}
\vspace{\topsep}
\sectionsep

\runsubsection{Hislop College, Nagpur}
\descript{ Maharashtra State Board,\\ Higher Secondary Examination, }
\location{2014 Percentage - 83\%}

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Internship Experiences}
\runsubsection{Full Stack Development Intern}
\descript{\newline \href{https://flytbase.com/}{FlytBase, Pune}}
\location{May 2018 - Present}
\vspace{2mm}
\begin{tightemize}
 \item Working on products like FlytCloud, FlytSecurity, FlytLive and FlytOS which are used for deploying and managing private drone fleet. 
 \item Worked extensively with Google Maps and Airmap. Worked on streaming live drone feed using WebRTC. Integrated Stripe payment gateway. \end{tightemize}


\sectionsep

\runsubsection{Web Development Intern (Part-time)}
\descript{\newline \href{https://www.healthcoco.com/}{Healthcoco Technologies Pvt. Ltd, Nagpur}}
\location{Jan 2018 - March 2018}
\begin{tightemize}
 \item Working on integrating REST APIs and UI development of Admin App used for managing doctors, labs and clinics in AngualrJS. \item Working on integrating material design and session management in Patient App in Angular 4. \end{tightemize}


\sectionsep

\runsubsection{Web Development Intern}
\descript{\newline \href{https://www.healthcoco.com/}{Healthcoco Technologies Pvt. Ltd, Nagpur}}
\location{Nov 2017 - Dec 2017}

\begin{tightemize}
 \item Integrated some key modules like Patient Registration, Profile, Search doctors in the Patient App in Angular 2. \item Designed, developed and deployed website for a dental clinic in core PHP.\newline Visit - \href{http://www.kharedentalclinic.com}{Khare Dental}  \end{tightemize}
 
\sectionsep

\runsubsection{Web Development Intern}
\descript{\newline \href{http://www.vyako.com/}{Vyako Technologies Pvt. Ltd, Nagpur,}}
\location{January 2017 - June 2017}

\begin{tightemize}
 \item Worked on two projects in development stage - Human Resource Management System (HRMS) and Project Management. \item Responsible for development and integration of many important features in HRMS projects such as
Employee Management, Leave Management, Attendance Management
\end{tightemize}

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards} 
%\begin{tabular}{rll}
%2014	     & top 52/2500  & KPCB Engineering Fellow\\
%2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
%2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%2013	     & National  & Jump Trading Challenge Finalist\\
%2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%2010     & National & Comp. Soc. of India's National Programming Contest\\
%\end{tabular}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extra-curricular Activities} 
\vspace{3mm}
\begin{tightemize}
 \item Member of organising committee of tech events in technical festival of college.
 \item Member of core committee - GCOEA Developers club, member of ACM India nagpur chapter, Google developers group Pune, Mumbai.
 \item Currently taking Udacity courses on Machine Learning and AI.
 \item Hobbies: Programming, Watching movies,TV series and tech shows, Playing cricket and badminton,
Learning new things.
\end{tightemize}

\sectionsep

\end{minipage} 
\end{document}
